---
title: "Week 1 Exercise"
format: html
editor: visual
---

## Creating data

First, we create our data by sampling 100 items from the log normal distribution, with $\mu=5$ and $\sigma=0.5$ as shown below.

```{r, results='hide'}
library(tidyverse)
require(gridExtra)
log_norm_dist <- rlnorm(100, 5, 0.5)
```

## Plotting ggplot2 histograms

We proceed to plot histograms of our data using the ggplot2 package. We plot two histograms of our data, one with a linear y axis and one with a logarithmic y axis.

```{r}
lin_hist <- ggplot(as.data.frame(log_norm_dist), aes(x=log_norm_dist)) + geom_histogram(binwidth=20) + ggtitle("Linear scale")
log_hist <- ggplot(as.data.frame(log_norm_dist), aes(x=log_norm_dist)) + geom_histogram(binwidth = 20) + ggtitle("Logarithmic scale") + scale_y_log10()
grid.arrange(lin_hist, log_hist, ncol=2)
```

## Plotting violin plot

Finally we plot a violin plot of our data

```{r}
violin_plot <- ggplot(as.data.frame(log_norm_dist), aes(x=log_norm_dist, y=log_norm_dist)) + geom_violin()
violin_plot
```
